Making Soup: Preparing and Validating Molecular Simulations of the Bacterial Cytoplasm

### 2019-09-24 paper/virtual_cytoplasm_v2.tex
references in tex

\subsubsection{RNA fraction}
Transporter RNAs (tRNAs) account for 74\% of the dry weight of non-ribosomal RNAs \colorbox{red!50}{REF}. Thus, we chose to model the RNA presence in the cytoplasm with tRNA molecules. Specifically, we considered the tRNA(Phe) molecule as a representative of tRNAs due to the availability of a recent crystallographic structure~\cite{Byrne2015}.
The protein and RNA content of the total dry weight of \textit{E.coli} is 55\% and 2.9\%, respectively \colorbox{red!50}{REF}. That is, the total RNA weight corresponds to 5\% of the total protein weight. This protein/RNA weight ratio was used to calculate the correct number of tRNA(Phe) molecules that were added to the cytoplasm model \colorbox{red!50}{(Table XXX)}.

@@

It has been demonstrated that each of the force fields that are most widely used to perform molecular dynamics simulations of macromolecules have different results for highly concentrated amino acid solutions ~ \cite{andrews2013molecular}. Previous all-atom simulations of high scale cytoplasm models used parameters from the CHARMM family of force fields ~\cite{yu2016biomolecular,mcguffee2010diffusion}. In this work we use, for the first time, the AMBER force fields to study crowding effects on a cytoplasm model. All-atom explicit solvent molecular dynamics simulations have been reported for large-scale cytoplasm models of \textit{Mycoplasma genitalium} composed by 103 and 12 million atoms that were simulated for 20 and 60 \SI{}{\nano\second}, respectively ~\cite{yu2016biomolecular}. The cytoplasm model described in this work has 1.5 million atoms and was simulated for the total of \SI{3}{\micro\second}, an unprecedented time scale to study crowding effects on a heterogeneous cytoplasm model in atomic detail.

All crowders are as compact in the cytoplasm model as they are in dilute conditions (Figure \ref{fig:structural_integrity_chain}A). Despite this overall stability, three crowders (TufA, MetE and IcdA) displayed greater deviation from their crystallographic structure in the cytoplasm model when compared to the dilute condition, indicating that there was some degree of local unfolding (Figure \ref{fig:structural_integrity_chain}B). Interestingly, the flexibility profiles calculated considering the C$\upalpha$ for each chain of the elements of our cytoplasm model show that, in the crowded condition, most of the proteins (TufA, MetE, AhpC, CspC and Ppa) are slightly more flexible than in the dilute condition (Figure \ref{fig:rmsf}). This is in agreement with simulation ~\cite{feig2011variable} and experimental data ~\cite{miklos2011protein,wang2012macromolecular} showing that crowders can destabilize the native structure of proteins due to the numerous unspecific short-lived interactions that are formed between them in a crowded environment.

@@

To the best of our knowledge, there is only one work in the literature which studied large scale cytoplasm models that included metabolites with all-atom explicit solvent molecular dynamics ~\cite{yu2016biomolecular}. Although they didn't report aggregation, they mentioned that the translational diffusion of highly charged phosphate-containing metabolites was "much slower" than expected. They attributed this observation to non-specific interactions between such metabolites and proteins. Maybe aggregation also contributed to their slower diffusion but it was not evident during \SI{140}{\nano\second}, which was the length of their longest simulation.

>>>>

\subsubsection{RNA fraction}
Transporter RNAs (tRNAs) account for 74\% of the dry weight of non-ribosomal RNAs~\cite{phillips2012}. Thus, we chose to model the RNA presence in the cytoplasm with tRNA molecules. Specifically, we considered the tRNA(Phe) molecule as a representative of tRNAs due to the availability of a recent crystallographic structure~\cite{Byrne2015}.
The protein and RNA content of the total dry weight of \textit{E.coli} is 55\% and 2.9\%, respectively~\cite{phillips2012}. That is, the total RNA weight corresponds to 5\% of the total protein weight. This protein/RNA weight ratio was used to calculate the correct number of tRNA(Phe) molecules that were added to the cytoplasm model \tabref{tbl:soup_components}.

@@

It has been demonstrated that each of the force fields that are most widely used to perform molecular dynamics simulations of macromolecules have different results for highly concentrated amino acid solutions ~ \cite{andrews2013molecular}. Previous all-atom simulations of high scale cytoplasm models used parameters from the CHARMM family of force fields ~\cite{yu2016biomolecular,mcguffee2010diffusion}. In this work we use, for the first time, the AMBER force fields to study crowding effects on a cytoplasm model. All-atom explicit solvent molecular dynamics simulations have been reported for large-scale cytoplasm models of \textit{Mycoplasma genitalium} composed by 103 and 12 million atoms that were simulated for 20 and 60 \SI{}{\nano\second}, respectively~\cite{yu2016biomolecular}. The cytoplasm model described in this work has 1.5 million atoms and was simulated for the total of \SI{3}{\micro\second}, an unprecedented time scale to study crowding effects on a heterogeneous cytoplasm model in atomic detail.

All crowders are as compact in the cytoplasm model as they are in dilute conditions (Figure \ref{fig:structural_integrity_chain}A). Despite this overall stability, three crowders (TufA, MetE and IcdA) displayed greater deviation from their crystallographic structure in the cytoplasm model when compared to the dilute condition, indicating that there was some degree of local unfolding (Figure \ref{fig:structural_integrity_chain}B). Interestingly, the flexibility profiles calculated considering the C$\upalpha$ for each chain of the elements of our cytoplasm model show that, in the crowded condition, most of the proteins (TufA, MetE, AhpC, CspC and Ppa) are slightly more flexible than in the dilute condition (Figure \ref{fig:rmsf}). This is in agreement with simulation~\cite{feig2011variable} and experimental data~\cite{miklos2011protein,wang2012macromolecular} showing that crowders can destabilize the native structure of proteins due to the numerous unspecific short-lived interactions that are formed between them in a crowded environment.

@@

To the best of our knowledge, there is only one work in the literature which studied large scale cytoplasm models that included metabolites with all-atom explicit solvent molecular dynamics~\cite{Yu2016a}. Although they didn't report aggregation, they mentioned that the translational diffusion of highly charged phosphate-containing metabolites was "much slower" than expected. They attributed this observation to non-specific interactions between such metabolites and proteins. Maybe aggregation also contributed to their slower diffusion but it was not evident during \SI{140}{\nano\second}, which was the length of their longest simulation.
